BurgerTown Presents: Open Adcess

### 2017-04-27 paper-sponsorships.tex
updates
have you seen this boy?

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/ad.jpg}
\caption{Have you seen this boy?}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/ad.jpg}
\caption{Have you seen this boy? He's a great catch! He's not very bright, and he has your brother's thighs, those Goodman thighs. He's no Clark Gable, but he's \checkmark tall \checkmark detoxing from that juice craze, oh such a thrill \checkmark the doctors say he has sensory interests others find unusual \checkmark probably better with these checklists than I am \checkmark almost certainly willing to testify as an alibi, no questions asked. That's a rare attribute these days. That boy, I worry, though, I worry. He doesn't eat. But he's got no one, it kills me. You know, both of the Ableman kids, they had the Internet make the shidduch. I hope if I send this to these computer science people it gets on the line.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/cambridge.jpg}
\caption{Visit beautiful Cambridge, MA. ``Where class privilege goes to reproduce itself.''}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/lowell.jpg}
\caption{Visit Lowell, MA. ``Where}
\end{figure}
